Fusion Moves for Correlation Clustering

### 2014-11-10 paper/anytimefigure2.tex
fixed errors in 2 plots

%!TEX root = egpaper_for_review.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pgfplotsset{every axis legend/.append style={
at={(1.0,1.2)},
anchor=north east}} 
\begin{figure*}[p]
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[  mark size=1pt,
  restrict y to domain=0:4620,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  width = 1.0\columnwidth,
  scaled ticks = false,
  every axis legend/.code={\let\addlegendentry\relax} 
  ]
  \addplot[color=yellow,mark=o] table[x=time, y=PIVOT*]{data3/image-seg.data};    \addlegendentry{PIVOT-BOEM}  
  \anytimeplot{image-seg}
  \end{semilogxaxis}
  \end{tikzpicture}

  \caption{image-seg}\label{fig:at:image-seg}
  \end{subfigure}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
  \begin{subfigure}[b]{0.33\textwidth}
    \centering
    \begin{tikzpicture}
    \begin{semilogxaxis}[  mark size=1pt,
   % restrict y to domain=-6000:-4400,
    xlabel = {runtime},
    xmin = 0,
    xmax = 4100,
    width = 1.0\columnwidth,
    scaled ticks = false,
    every axis legend/.code={\let\addlegendentry\relax} 
    ] 
    \addplot[color=yellow,mark=o] table[x=time, y=PIVOT*]{data3/knott-3d-150.data};          \addlegendentry{PIVOT-BOEM}
    \anytimeplot{knott-3d-150}

>>>>

%!TEX root = egpaper_for_review.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pgfplotsset{every axis legend/.append style={
at={(1.0,1.2)},
anchor=north east}} 
\begin{figure*}[p]
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[  mark size=1pt,
  %restrict y to domain=0:4620,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  width = 1.0\columnwidth,
  scaled ticks = false,
  every axis legend/.code={\let\addlegendentry\relax} 
  ]
  \addplot[color=yellow,mark=o] table[x=time, y=PIVOT*]{data3/image-seg.data};    \addlegendentry{PIVOT-BOEM}  
  \anytimeplot{image-seg}
  \end{semilogxaxis}
  \end{tikzpicture}

  \caption{image-seg}\label{fig:at:image-seg}
  \end{subfigure}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
  \begin{subfigure}[b]{0.33\textwidth}
    \centering
    \begin{tikzpicture}
    \begin{semilogxaxis}[  mark size=1pt,
   % restrict y to domain=-6000:-4400,
    xlabel = {runtime},
    xmin = 0,
    xmax = 100,
    width = 1.0\columnwidth,
    scaled ticks = false,
    every axis legend/.code={\let\addlegendentry\relax} 
    ] 
    \addplot[color=yellow,mark=o] table[x=time, y=PIVOT*]{data3/knott-3d-150.data};          \addlegendentry{PIVOT-BOEM}
    \anytimeplot{knott-3d-150}

### 2014-11-10 paper/inputs/fig_fusion.tex
fixed errors in 2 plots

            \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt]
            (1-2,3.5) -- (1-2,6.5) node [black,midway,xshift=-1.2cm,rotate=90,align=left] 
            {proposal edge \\ labeling $\bm{x'}$};

            \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt]
            (1-2,3-3.5) -- (1-2,6.5-4) node [black,midway,xshift=-1.2cm, rotate=90,align=left] 
            {proposal edge \\ labeling $\bm{x''}$};

            \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt]
            (5,3.5) -- (5,6.5) node [black,midway,xshift=-1.2cm,rotate=90,align=left] 
            {proposal node \\ labeling $\bm{l'}$};

            \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt]
            (5,3-3.5) -- (5,6.5-4) node [black,midway,xshift=-1.2cm, rotate=90,align=left] 
            {proposal node \\ labeling $\bm{l''}$};

            \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt]
            (5,-4.5) -- (5,-1.5) node [black,midway,xshift=-1.2cm, rotate=90,align=left] 
            {Binary fusion \\ move problem};

@@

            \draw (2+8,2-4) node[nD, circle split part fill={red!60, red!60}] (n0) {$ $}; 
            \draw (4+8,2-4) node[nD, circle split part fill={red!60, blue!60}] (n1) {$ $};
            \draw (2+8,0-4) node[nD, circle split part fill={green!60, red!60}] (n3) {$ $}; 
            \draw (4+8,0-4) node[nD, circle split part fill={green!60, green!60}] (n4) {$ $};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

@@

            \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0.8cm]
            (5,-6) -- (33,-6) node [black,midway,xshift=0cm,yshift=-1cm] 
            {
                For all different colorings $l''$, the binary fusion move subproblem is different.
            };

            \draw [decorate,decoration={brace,amplitude=10pt,raise=4pt},yshift=0.8cm]
            (5,2) -- (33,2) node [black,midway,xshift=0cm,yshift=1cm] 
            {
                All these node labelings encode the same partition
            };

@@

    \end{tikzpicture}
}
\caption{
w
}\label{fig:fusion_abiguty}
\end{figure*}
\end{center}

>>>>

            \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt]
            (1-2,3.5) -- (1-2,6.5) node [black,midway,xshift=-1.2cm,rotate=90,align=left] 
            {\Large{proposal edge} \\ \Large{labeling \quad $\bm{x'}$}};

            \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt]
            (1-2,3-3.5) -- (1-2,6.5-4) node [black,midway,xshift=-1.2cm, rotate=90,align=left] 
            {\Large{proposal edge} \\ \Large{labeling \quad $\bm{x''}$}};

            \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt]
            (5,3.5) -- (5,6.5) node [black,midway,xshift=-1.2cm,rotate=90,align=left] 
            {\Large{proposal node} \\ \Large{labeling \quad $\bm{l'}$}};

            \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt]
            (5,3-3.5) -- (5,6.5-4) node [black,midway,xshift=-1.2cm, rotate=90,align=left] 
            {\Large{proposal node} \\ \Large{labeling \quad $\bm{l''}$}};

            \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt]
            (5,-4.5) -- (5,-1.5) node [black,midway,xshift=-1.2cm, rotate=90,align=left] 
            {\Large{Binary fusion} \\ \Large{move problem}};

@@

            \draw (2+8,2-4) node[nD, circle split part fill={red!60, red!60}] (n0) {$ $}; 
            \draw (4+8,2-4) node[nD, circle split part fill={red!60, blue!60}] (n1) {$ $};
            \draw (2+8,0-4) node[nD, circle split part fill={green!60, red!60}] (n3) {$ $}; 
            \draw (4+8,0-4) node[nD, circle split part fill={green!60, blue!60}] (n4) {$ $};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

@@

            \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0.8cm]
            (5,-6) -- (33,-6) node [black,midway,xshift=0cm,yshift=-1cm] 
            {
                \Large{For all different colorings $\bm{l''}$, the binary fusion move subproblem is different.}
            };

            \draw [decorate,decoration={brace,amplitude=10pt,raise=4pt},yshift=0.8cm]
            (5,2) -- (33,2) node [black,midway,xshift=0cm,yshift=1cm] 
            {
                \Large{All these node labelings encode the same partition}
            };

@@

    \end{tikzpicture}
}
\caption{
todo: write me (why normal fusion does not work)
}\label{fig:fusion_abiguty}
\end{figure*}
\end{center}
